Tables/Graphs for Article

### 2018-01-22 article/draft1.tex
edits from Shannon

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.

@@

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock} also determined that textual features (e.g. word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{H.fu} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a} \cite{Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.

@@

% Table of derived predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{2cm} | L{10cm} |}
  \hline
  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
  & If the question's text is in all lower case \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
  & If the question's title ends in a question mark \\ \cline{2-2}
  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & If the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
  & Average frequency for all of a question's tags. Frequency defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a value of 0 (Average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (Text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name (Device name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
\end{tabular}
\caption{Categorical and continuous variables derived}
\label{table:variables}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name and category, title, text, tags, If the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. See Appendix for an example of an answered and unanswered question. Variables derived can be found in Table \ref{table:variables}. See Appendix for details on variable derivation.

@@

As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univariate Cox models and strength of association with response times was assessed. Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.  Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.

In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Significant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{Oakes1981}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

To compute predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

@@

  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data). Of those questions, 4,951 (63.8}\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2,159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

  Figure ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.

@@

This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times. This variable is the average frequency, or proportion of times a question's tags appear in all of the data set. If a question has a higher average, than at least one of its tags are considered frequently-used. This variable was created based off of findings from \cite{Bhat2014}.

>>>>

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.

@@

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock} also determined that textual features (e.g. word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{H.fu} instead found that non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate that a question is of high quality also lead to faster response times.

@@

% Table of derived predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{2cm} | L{10cm} |}
  \hline
  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
  & If the question's text is in all lower case \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
  & If the question's title ends in a question mark \\ \cline{2-2}
  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & If the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name dDevice name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
\end{tabular}
\caption{Categorical and continuous variables derived}
\label{table:variables}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name, device category, question title, text, tags, new user status, date and time the question was posted, and date and time the first answer was received. Variables derived can be found in Table \ref{table:variables}. The Appendix contains details on variable derivation, as well as an example of an answered and unanswered question in Table \ref{table:questions}.

@@

As the probability distribution for response times is unknown, a non-parametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univariate Cox models and the evidence of association with response times was assessed. Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.  Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimal number of knots \cite{Harrell2015}. All predictors found to be significant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.

In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Significant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $\chi^2$ distribution \cite{Oakes1981}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

All computation was executed under \texttt{R} version 3.4.3.  \hl{Package for KM curve?} To compute predicted survival probabilities using the model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package in R. This function uses the Cox model and a vector of times to compute predicted survival probabilities. \hl{Include reference for data and functions in oshitaR pacakge?}

@@

  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data). Of those questions, 4,951 (63.8}\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2,159.02 hours (89.96 days). Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

  Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.

@@

This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times. This is computed as the average frequency, or proportion of times, a question's tags appear in all of the data set. Questions without tags were assigned a value of 0.  If a question has a higher average, then at least one of its tags are considered frequently-used. This variable was created based off of findings from \cite{Bhat2014}.
